Loss recovery and tail loss performance in Multipath TCP

### 2016-12-18 main.tex
Update

\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth]{images/fortest.pdf}
\caption{Topology used for Emulation}\label{fig1}
\end{center}
\end{figure}
\begin{center}

@@

In Linux, TCP retransmission features are controlled by a sysctl setting tcp.early.retrans. It has 5 possible values with ranging from 0 to 4 with 3 being Linux default, enables both
ER and TLP. For this analysis, we used 0,3 and 4. In each setting, we calculate burst completion time for two burst of 80 packets each. The setup has server and client with MPTCP
enabled linux running on them. Client has two wireless interfaces with one way delay on each interface ranging from 20ms to 120ms. We consider 5 scenarios with delay pairings 20ms-20ms
20ms-30ms, 20ms-120ms, 30ms-20ms, 120ms-20ms to understand the effect of delay difference in the performance. The expected retransmission behavior for different settings of ER is shown 
in~\ref{timingER0},~/\ref{timingER3} and ~\ref{timingER4}.

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=610, natheight=400]{images/timingER0.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=0}\label{timingER0}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=610, natheight=400]{images/timingER3.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=3}\label{timingER3}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=610, natheight=400]{images/timingER4.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=4}\label{timingER4}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth,natwidth=578.16,natheight=433.62]{plots/1P.pdf}
\caption{Single packet tail loss}\label{1p}
\end{center}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth,natwidth=578.16,natheight=433.62]{plots/2P.pdf}
\caption{Two packet tail loss}\label{2p}
\end{center}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=578.16,natheight=433.62]{plots/1PP.pdf}
\caption{Single packet tail loss together with probe loss}\label{1pp}
\end{center}
\end{figure}

>>>>

\documentclass[10pt,draftcls,twocolumn]{IEEEconf}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth]{images/fortest.pdf}
\caption{Topology used for Emulation}\label{fig1}
\end{center}
\end{figure}
\begin{center}

@@

In Linux, TCP retransmission features are controlled by a sysctl setting tcp.early.retrans. It has 5 possible values with ranging from 0 to 4 with 3 being Linux default, enables both
ER and TLP. For this analysis, we used 0,3 and 4. In each setting, we calculate burst completion time for two burst of 80 packets each. The setup has server and client with MPTCP
enabled linux running on them. Client has two wireless interfaces with one way delay on each interface ranging from 20ms to 120ms. We consider 5 scenarios with delay pairings 20ms-20ms
20ms-30ms, 20ms-120ms, 30ms-20ms, 120ms-20ms to understand the effect of delay difference in the performance.

Figures ~\ref{t1p,t2p,t1pp} represent the comparison of TCP burst completion times for the two bursts from server to client.

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth,natwidth=578.16,natheight=433.62]{plots/T1P.pdf}
\caption{Single packet tail loss using TCP}\label{t1p}
\end{center}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth,natwidth=578.16,natheight=433.62]{plots/T2P.pdf}
\caption{Two packet tail loss using TCP}\label{t2p}
\end{center}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth, natwidth=578.16,natheight=433.62]{plots/T1PP.pdf}
\caption{Single packet tail loss together with probe loss using TCP}\label{t1pp}
\end{center}
\end{figure}

The expected retransmission behavior for different settings of ER is shown 
in~\ref{timingER0},~/\ref{timingER3} and ~\ref{timingER4}.

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth, natwidth=610, natheight=400]{images/timingER0.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=0}\label{timingER0}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth, natwidth=610, natheight=400]{images/timingER3.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=3}\label{timingER3}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth, natwidth=610, natheight=400]{images/timingER4.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=4}\label{timingER4}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth,natwidth=578.16,natheight=433.62]{plots/1P.pdf}
\caption{Single packet tail loss using MPTCP}\label{1p}
\end{center}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth,natwidth=578.16,natheight=433.62]{plots/2P.pdf}
\caption{Two packet tail loss using MPTCP}\label{2p}
\end{center}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth, natwidth=578.16,natheight=433.62]{plots/1PP.pdf}
\caption{Single packet tail loss together with probe loss using MPTCP}\label{1pp}
\end{center}
\end{figure}
